Nail: A practical interface generator for data formats

### 2014-04-03 paper/relwk.tex
minor

Nail improves upon Hammer in three ways. First, Nail  generates output besides recognising input.
Second, Nail does not require the programmer to write potentially insecure semantic actions. Last,
Nail's structural dependencies allow it to work with protocols Hammer cannot recognise, such as
protocols with offset fields or length fields (Hammer has extremely limited support for length
fields. It can parse arrays immediately preceeded by their length).

>>>>

Nail improves upon Hammer in three ways. First, Nail  generates output besides recognising input.
Second, Nail does not require the programmer to write potentially insecure semantic actions. Last,
Nail's structural dependencies allow it to work with protocols Hammer cannot recognise, such as
protocols with offset fields or length fields (Hammer has extremely limited support for length
fields: it can parse arrays immediately preceeded by their length).
